Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2014-01-29 unstructured.tex
2013.03.29 (Alex) Section on unstructured algorithms, massively reworked (from formatting to phrasing). Minor updates to background and conclusion sections.

\section{Unstructured P2P Networks}
\label{section:unstructured}

This section is dedicated to unstructured P2P networks. Algorithms
for tackling the topology mismatch problem in such
networks are discussed, analyzed, and categorized based on the use of the
overlay structure, the message forwarding approach for peer communication, and
techniques proposed for detecting proximity in order to optimize overlay
topology.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Improving search in peer-to-peer networks}

@@

\cite{YG-M2002} proposes an easy to implement and practical solution to the
inefficiency of Gnutella's ``blind flooding'' approach. The paper introduces
three different forwarding methods, namely \emph{iterative deepening},
\emph{directed BFS}, and \emph{local indices}.

In iterative deepening, %(see Figure~\ref{figure:dbfs:iterdeep})
the search is
performed on a BFS tree with multiple preset depths. The depth limit is
iteratively increased by the source node for each query, based on the quality of
the results. The source node may issue a new request with increased depth limit
that will trigger the nodes at the last depth level to resume the search. The
iterative approach avoids restarting the whole search process from scratch at
each iteration and reduces the load of the nodes on the upper levels of the
tree. Its major drawback is the delay between successive iterations, as the
source node needs to examine the results at each iteration before deciding to
quit or resume the query.

The directed BFS
tries to avoid this delay by forwarding the query messages only to a select
set of neighbors, in which the selection criteria varies from the number of
results received previously, distance in terms of hops, bandwidth, or the query
load of the neighbor.

In local indices
each node
indexes data within a radius of $r$ hops and uses this local index to answer
queries on behalf of them without generating additional traffic. Local indices
greatly reduce the aggregate bandwidth usage of the network and improves query
efficiency, however, updating the indices in cases with frequent node joins and
leaves introduces a serious overhead into the system if the radius is kept broad.

% \begin{center}
% \begin{tabular}{ccc}
% \textbf{Efficiency} & \textbf{Overhead} & \textbf{Scalability} \\
% \hline
% Iterative Deepening & ? & ? & ?
% Directed BFS & ? & ? & ?
% Local Indices & ? & ? & ?
% \end{tabular}
% \end{center}
\begin{center}
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Iterative Deepening} &
% needs recalculation in every iteration step
% extra delay imposed in a high churn environment that prohibits the algorithm
% to start from the last level of nodes and results in a restart of the whole
% process
low &
% the process in not started from the beginning at each iteration step
low &
% 
medium \\
\emph{Directed BFS} &
% Better time to satisfaction compared to iterative deepening
medium &
% Better quality and quicker results mean more aggregate bandwidth and
% processing power needs to be consumed since more nodes are involved (death
% spirral).
medium &
% BFS is Gnutella's non efficient communication method
medium \\
\emph{Local Indices} &
% efficiency is enhanced greatly since data pointers are replicated across the
% network
high &
% updating indices is a time and resource consuming process.
medium &
% the scalability is constrained by the indices update in a highly dynamic
% environment (high churn)
medium \\
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{ \bf Delay Aware P2P System}
A new \emph{Delay Aware P2P System (DAPS)} is introduced in \cite{ZL2005}. Its
main goal is to reduce the time of a look-up request by dividing the routing
tables of peers into several sectors of increasing delay. The source node
emitting the query message defines a delay boundary or the \emph{pruning
factor} in the paper's context. Request messages are then forwarded only to
nodes whose delay is less than or equal that boundary. 
%With the clustered
%routing tables and the loose organization of DAPS' overlay network it is
%considered by is between structured and unstructured.

% TODO: MAYBE REVIEW THE EVALUATION
\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
low &
%
low &
%
medium
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Gia}
\emph{Gia} \cite{CRBLS2003} is an effort to solve the scalability
problem of the unstructured P2P file sharing systems, in particular Gnutella.
The main novelty in the design of Gia is the replacement of the blind flooding
approach of Gnutella with random walks \cite{lv_randomwalks_2002}. Although
random walks is a step in the right direction, issuing only a single copy of the
query within the network reduces the search scope, thus affecting negatively the
success rate of the query.  In order to overcome this limitation, Gia introduces
a token-based flow control mechanism, which is essentially an intelligent flow
control algorithm that gradually redirects the queries to nodes which are more
likely to answer. In order to prevent overloading of nodes with query requests,
Gia uses a token-based flow control algorithm in which each node announces the
number of query requests it can handle in terms of tokens to its neighbors, so
that neighbors only forward query requests to nodes that they previously
received tokens from. Gia also acknowledges the heterogeneity in peer bandwidth,
processing power, disk speed, etc, of the nodes in P2P networks and uses this
information when connecting nodes to each other and by using a topology
adaptation algorithm, Gia ensures that high capacity nodes have high degrees and
low capacity nodes are within short proximity to high capacity ones.
% TODO: THIS FOLLOWING REMARK SOUNDS LIKE THE ALGORITHM SHOULDN'T BE IN THIS
%       SURVEY AFTER ALL!!
Although the topology adaptation algorithm Gia uses improves the scalability of
the network, it does not help much in solving the topology mismatch problem,
since it does not consider the underlying physical topology.

%
%More specifically, there are four key components in the design of
%\emph{Gia} which are summarized bellow:
%\begin{enumerate}
%  \item A \emph{dynamic topology adaptation} protocol that puts
%participating nodes within short reach of high capacity nodes so that these
%\emph{high-degree} nodes, which due to their high connectivity receive most of
%the queries, actually have the capacity to handle them.
%  \item An \emph{active flow control} scheme is used to avoid overloaded
% hot-spots. Heterogeneity is detected and flow control tokens are given to
%nodes based on the available capacity.
%  \item Every node maintains pointers to to the content that is offered by
% their immediate neighbors, creating a \emph{one-hop replication} of pointers,
%scheme.
%  \item A \emph{search protocol} based on random walks, that is biased towards
% directing queries to high-capacity nodes that are typically best able to
%answer these queries.
%\end{enumerate}
%

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Drastically reduces the search scope.
low &
% Only one copy of the query is issued to the network.
% A token based flow control mechanism redirects queries to nodes that are most
% likely to fulfill them.
low &
% Even thought the low overhead scalability is reduced by the reducing of
% search scope.
medium
\end{tabular}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Distributed Cycle Minimization Protocol (DCMP)}
We have already discussed that blind flooding often causes messages to be routed in a direction
that is far from the path that can
ultimately fulfill the query request. Another problem with topology unaware
systems is the duplication of messages due to cycles, even along the correct
forwarding path. The authors of \cite{ZKB2008} focused on that exact deficiency
of overlay networks and introduced Distributed Cycle Minimization Protocol
(DCMP), a dynamic, fully distributed method to remove cycles without sacrificing
overlay connectivity, resilience and other important properties of unstructured
architectures by avoiding a hierarchical organization of peers. In DCMP, once a
cycle is detected, the most powerful node in that cycle is elected as the
\emph{Gate Peer} and the cycle is then broken at a strategic place so that it
will result in the minimization of the distance between the Gate Peer and all
other nodes that participated in that cycle. The process is managed by using two
special message types namely \emph{Information Collection (IC)} and \emph{Cut
Message (CM)}. One disadvantage of DCMP is that since the distance a forwarded
message can travel is limited by the TTL value, which is practically $7$ in most
cases, DCMP cannot detect cycles formed by more than 7 peers. Even though cycle
elimination improves the network performance, it does not actually solve the
topology mismatch problem.

%
%\subsection{Distributed Cycle Minimization Protocol}
%
%\paragraph{}
%The first step after detecting a duplicate message by some peer is to gather
% information from all peers in the cycle using a new type of control message
%called \emph{Information Collecting Message} or \emph{ICM}. ICM contains:
%\begin{inparaenum}[\itshape i\upshape)]
%  \item a \emph{GUID}\footnote{Globally Unique Identifier assigned to every
% query message generated by any node.} field same as the one of the duplicate
%message,
%  \item \emph{DetectionID} field which represents the direction of the
% connection where the duplicate was identified\footnote{This ensures the
%uniqueness of the ICM messages because as it travels through many cyclic paths,
%multiple peers will detect the duplicates and initiate an ICM message.}, and
%  \item \emph{Node Information Vector (NIV)} which contains information
% (bandwidth, CPU power, etc) about peers that propagated the ICM.
%\end{inparaenum}
%
%\paragraph{}
%Suppose $A$ detected the duplicate as depicted in Figure~\ref{figure:dcmp}. It
% then emits an ICM to $B$ and $F$, that initially contains information only
%about itself. Each peer that receives the ICM, appends its information and
%propagates it along the reverse path of the original message. Since two copies
%of ICM are sent, at some point, a peer, say peer $D$, will receive a duplicate
%ICM. Using the information in the NIVs of the ICMs, $D$, decides to cut (for
%example) the EF connection. To inform the other peers about its decision, it
%emits a \emph{Cut Message (CM)} which contains the GUID and DetectionID of the
%corresponding ICM and an additional field that identifies the connection to be
%cut. $D$, then, forwards the CM in the reverse directions from where the ICM
%arrived. Similarly CMs received by any peer are propagated toward the reverse
%path of the corresponding ICM. Eventually, either peer $E$ or peer $F$ will
%receive the CM and cut the connection, thus eliminating the cycle.
%
%Receiving a duplicate ICM denotes the existence of a cycle. The opposite is not
% true though. For example, if the cycle contains $2 \times TTL$ edges, it will
%not be detected, because the ICM messages will be discarded before they locate
%it. There is a trade-off between preserving the connectivity of the network and
%minimizing the duplicates that makes such a possibility to be safely ignored.
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/dcmp.jpeg}
%\caption{Cycle elimination methods in DCMP}
%\label{figure:dcmp}
%\end{figure}
%
%\paragraph{}

%
% TODO: SOME DISCUSSION
%
%Actually, the duplicate packet problem seems to hurt more the active nodes;
%those with higher capacities and bandwidth that contribute the most to the
%network.
%

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It return more result than LTM according to experiments in
% \cite{ZKB2008}
medium &
% Duplicates are an important fraction of the redundant overhead imposed by
% topology mismatch and thus DCMP minimizes this as possible.
% The control overhead is also one to two orders of magnitude less than LTM due
% to its ``lazy'' broadcasting of control messages (as opposed to LTM's periodic
% approach) - \cite{ZKB2008}
low &
% fully distributed method
high
\end{tabular}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Replication Strategies in Unstructured Peer-to-Peer Networks}
\cite{CS2002} aim to improve the inefficient blind search algorithm by
replicating the data in a P2P network. The main intuition behind the
idea of replication, or using cached copies, is that as the number of copies for
each item increases in the network, it would be easier for a search algorithm,
even a random one, to locate these items. To analyze the feasibility of
such an approach, the authors investigate three different replication
strategies, namely uniform, proportional, and square root allocation. In the
uniform model, the copies of items are uniformly replicated in the network,
while in the proportional model, the items are replicated based on their query
rate, so that frequently queried items are replicated more. The square root
allocation is a strategy proposed by Cohen and Shenker, which is a model between
the uniform and proportional allocation.  To evaluate the outcome of
the replication models, the overall costs of successful and unsuccessful
searches in the network are compared. Results argue that the uniform allocation
model minimizes the maximum search size, therefore reduces the time spent on an
unsuccessful search. The proportional model, on the other hand, promotes the
more frequently queried items by replicating them more and therefore decreases the
search time for popular items, but suffers when needing to locate the rare
items. The authors also claim that the expected successful search size is the
same for uniform and proportional models, and any approach between them would
always behave much better. Finally, they propose the square root allocation
approach, which is a replication strategy that minimizes the expected search
size of successful queries in P2P networks.

\begin{center}
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Uniform Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% When item is created, replicate its key in a fixed number of hosts.
low &
%
medium \\
\emph{Proportional Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% for each query, replicate the key in a fixed number of hosts (need to know or
% estimate the query rate)
medium &
%
low \\
\emph{Square Root Replication Allocation} &
% All (strictly) in-between strategies are (strictly) better than Uniform and
% Proportional - replication theory
medium &
% Assuming that each query keeps track of the search size then each time a query
% is finished the object is copied to a number of sites proportional to the
% number of probes that the search required.
medium &
% e.g. path replication is easy to scale, just detect the path along which the
% query ultimately got fulfilled
medium \\
\end{tabular}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Narada}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Landmark Binning (LM)}\label{sec:landmark_binning}
% \begin{figure*}
% \centering
%   \includegraphics[scale=0.4]{img/algorithms/landmark_binning}
% \caption{Example 2D coordinate overlay and a sample routing path from node D to
% (x,y).}
% \label{fig:landmark_binning}
% \end{figure*}

>>>>

\section{Unstructured \p\ Networks}
\label{section:unstructured}

In this section, we present algorithms that tackle the topology mismatch
problem in unstructured \p\ networks and classify them based on their 
use of the overlay structure, their message forwarding scheme 
for peer communication as well as techniques used for detecting proximity 
in order to optimize their overlay topology.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Improving search in peer-to-peer networks}

@@

To improve over {\sl Gnutella}'s ``blind flooding'' approach,
\cite{YG-M2002} proposed a practical and easy to implement solution 
weaved around three different message forwarding methods:
\emph{iterative deepening},
\emph{directed BFS}, and \emph{local indices}.
%%AD local indices is not "a message forwarding method" really...  but ok.

In \emph{iterative deepening}, 
%(see Figure~\ref{figure:dbfs:iterdeep})
the search is
performed on a BFS tree with multiple preset depths. 
The depth limit is iteratively increased by the source node for each query, 
based on the quality of the results. 
The source node may issue a new request with increased depth limit
that will trigger the nodes at the last depth level to resume the search. 
The iterative approach avoids restarting the entire search process 
from scratch at each iteration and reduces the load on the nodes of 
the upper levels of the tree. 
Its major drawback is the delay between successive iterations, as the
source-node has to examine the results at each iteration before deciding to
either quit or resume the query.

The \emph{directed BFS}
tries to avoid the aforementioned delay by forwarding 
the query messages only to a select set of neighbors, in which the selection criteria varies from the number of
results received previously, distance in terms of hops, bandwidth, or the query
load of the neighbor.
%
In \emph{local indices},
each node indexes data within a radius of $r$ hops and uses 
this local index to answer queries % on behalf of them 
without generating additional traffic. Local indices
greatly reduce the aggregate bandwidth usage of the network and 
improve query efficiency. However, updating such indices in 
the presence of frequent node joins/departures 
may introduces significant overhead should the radius is kept broad.
Below, we outline how the techniques in~\cite{YG-M2002}
fare against the $3$ major performance criteria 
of Section~\ref{section:background}.
% \begin{center}
% \begin{tabular}{ccc}
% \textbf{Efficiency} & \textbf{Overhead} & \textbf{Scalability} \\
% \hline
% Iterative Deepening & ? & ? & ?
% Directed BFS & ? & ? & ?
% Local Indices & ? & ? & ?
% \end{tabular}
% \end{center}
\begin{center}
{\footnotesize
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Iterative Deepening} &
% needs recalculation in every iteration step
% extra delay imposed in a high churn environment that prohibits the algorithm
% to start from the last level of nodes and results in a restart of the whole
% process
low &
% the process in not started from the beginning at each iteration step
low &
% 
medium \\
\emph{Directed BFS} &
% Better time to satisfaction compared to iterative deepening
medium &
% Better quality and quicker results mean more aggregate bandwidth and
% processing power needs to be consumed since more nodes are involved (death
% spiral).
medium &
% BFS is Gnutella's non efficient communication method
medium \\
\emph{Local Indices} &
% efficiency is enhanced greatly since data pointers are replicated across the
% network
high &
% updating indices is a time and resource consuming process.
medium &
% the scalability is constrained by the indices update in a highly dynamic
% environment (high churn)
medium \\
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \paragraph*{ \bf Delay Aware P2P System}
% A new \emph{Delay Aware P2P System (DAPS)} is introduced in \cite{ZL2005}. 
A \emph{delay--aware} \p\ system termed {\sl DAPS} 
was introduced in~\cite{ZL2005}.
{\sl DAPS}  seeks to attain reduced look-up times by dividing 
peer routing tables into several sectors of increasing delay. 
The source node that issues the query designates the delay 
boundary it may tolerate providing so a \emph{pruning factor}.
In this context, user requests are forwarded only to 
nodes whose expected delay is less than or equal to the indicated boundary. 
{\sl DAPS} primarily focuses on user ``experience'' and deploys a
end-to-end delay monitoring mechanism that  may enable
the clustering of routing tables. 
In an dynamic environment, the formation 
of very accurate such routing tables might be however an elusive goal.
%With the clustered
%routing tables and the loose organization of DAPS' overlay network it is
%considered by is be tween structured and unstructured.
%%
% TODO: MAYBE REVIEW THE EVALUATION
In terms of the $3$ performance criteria, {\sl DAPS} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
low &
%
low &
%
medium
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Gia}

The key objective of the {\sl Gia} system~\cite{CRBLS2003} is 
to help alleviate the scalability omnipresent
in unstructured \p\ file-sharing systems.
At first, {\sl Gia} replaced {\sl Gnutella}'s blind flooding 
with random walks.
Although this adoption was 
a step in the right direction~\cite{lv_randomwalks_2002},
issuing a single copy of the query within the network
effectively reduces the search scope and may negatively affect 
the success rate of the query in question.
To overcome this limitation, {\sl Gia} introduces
a token-based flow control mechanism
% , which is essentially an intelligent flow control algorithm 
%%AD what is "intelligent"?? - I think you can live without this above line... 
that gradually redirects queries to nodes which are more
likely to answer. 
%%
This flow control mechanism also helps prevent node overloading
as each peer ``announces'' the number of query requests it 
can handle in terms of tokens to its neighbors; to this end, 
peers only forward query requests to nodes that they previously
received tokens from.
%%AD changed below as above... I have the impression that this token 
%%	based mechanism is one and the same (the way the writing appeared 
%%	was that they were two mechanisms!  check!!!
%%%%
% In order to prevent overloading of nodes with query requests,
% Gia uses a token-based flow control algorithm in which each node announces the
% number of query requests it can handle in terms of tokens to its neighbors, so
% that neighbors only forward query requests to nodes that they previously
% received tokens from. 
%%%%%%%%%%%%%%%%%
{\sl Gia} also acknowledges the heterogeneity in peer bandwidth,
processing power, disk speed, etc., of \p\ nodes and uses this
information when connecting nodes to each other.
By using a topology adaptation algorithm, 
{\sl Gia} places low capacity nodes within 
short proximity to peers with high performance features.
This topology adaptation algorithm is based on the metric 
each node maintains about its satisfaction --ranging between $0$ and $1$--
for the neighbors it finds itself associated with. 
Through message exchange, a peer can establish new connections 
or drop superseded one in order to improve its satisfaction.
%%AD the 2 lines below make no sense.. I rephrased as above... 
% \emph{Gia} ensures that high capacity nodes have high degrees and
% low capacity nodes are within short proximity to high capacity ones.
%%%%%%%%AD this (above) phrase is almost verbatim out of the paper! NO good idea ;-)
Despite the fact that {\sl Gia}'s topology adaptation algorithm 
that primarily focuses on the satisfaction of peers improves the network's 
scalability, it falls short in addressing the mismatch problem
as considerations for the underlying network are not handled in explicit
terms.
%%AD the comment TODO is somewhat correct. Changed the wording here..... 
% TODO: THIS FOLLOWING REMARK SOUNDS LIKE THE ALGORITHM SHOULDN'T BE IN THIS
%       SURVEY AFTER ALL!!
% Although the topology adaptation algorithm Gia uses improves the scalability of
% the network, it does not help much in solving the topology mismatch problem,
% since it does not consider the underlying physical topology.
%
%More specifically, there are four key components in the design of
%\emph{Gia} which are summarized bellow:
%\begin{enumerate}
%  \item A \emph{dynamic topology adaptation} protocol that puts
%participating nodes within short reach of high capacity nodes so that these
%\emph{high-degree} nodes, which due to their high connectivity receive most of
%the queries, actually have the capacity to handle them.
%  \item An \emph{active flow control} scheme is used to avoid overloaded
% hot-spots. Heterogeneity is detected and flow control tokens are given to
%nodes based on the available capacity.
%  \item Every node maintains pointers to to the content that is offered by
% their immediate neighbors, creating a \emph{one-hop replication} of pointers,
%scheme.
%  \item A \emph{search protocol} based on random walks, that is biased towards
% directing queries to high-capacity nodes that are typically best able to
%answer these queries.
%\end{enumerate}
%
In terms of the $3$ stated criteria, {\sl Gia}'s approach is as follows:
%%
%%AD from the discussion I think that Efficiency might me medium-how??? 
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Drastically reduces the search scope.
low &
% Only one copy of the query is issued to the network.
% A token based flow control mechanism redirects queries to nodes that are most
% likely to fulfill them.
low &
% Even thought the low overhead scalability is reduced by the reducing of
% search scope.
medium
\end{tabular}
}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Distributed Cycle Minimization Protocol (DCMP)}
% We have already discussed that blind flooding often causes messages 
% to be routed in a direction
% that is far from the path that can
% ultimately fulfill the query request. 
%%AD the above is just repetition...

Another problem with topology unaware
systems is the duplication of messages due to cycles that appears 
 even along the correct forwarding path. 
\cite{ZKB2008}~focuses on this exact deficiency
of overlay networks and introduces the \emph{Distributed Cycle Minimization Protocol
(DCMP)}, a dynamic, fully distributed method that removes cycles;
this is accomplished without sacrificing
overlay connectivity, resilience and other key properties of unstructured
\p\ architectures and by avoiding a hierarchical organization of peers. 
Once a cycle is detected in {\it DCMP}, the most powerful node in that cycle 
is elected as the \emph{Gate Peer} and the cycle is then broken 
%% at a strategic place  %%AD I am not sure what this adds?? strategic?? on what??
so that it results in the minimization of the distance between the 
\emph{Gate Peer} and all other nodes that are currently part of the cycle. 
This process is managed by using two specialized message types 
namely, \emph{Information Collection (IC)} and \emph{Cut Message (CM)}. 
\emph{DCMP} bases its operation on messages whose travel is limited by 
imposed $TTL$ whose maximum value is set at  $7$ for most cases. 
This inherently limits the protocol as \emph{DCMP} is unlikely that 
can efficiently detect cycles that span for more than $7$ nodes.
%%AD rephrased as above
% One disadvantage of DCMP is that since the distance a forwarded
% message can travel is limited by the TTL value, which is practically $7$ in most
% cases, DCMP cannot detect cycles formed by more than 7 peers. 
Even though cycle elimination does improve network performance, 
it cannot 
% actually solve 
directly contribute in the solution of 
the topology mismatch problem.
%%
%
%\subsection{Distributed Cycle Minimization Protocol}
%
%\paragraph{}
%The first step after detecting a duplicate message by some peer is to gather
% information from all peers in the cycle using a new type of control message
%called \emph{Information Collecting Message} or \emph{ICM}. ICM contains:
%\begin{inparaenum}[\itshape i\upshape)]
%  \item a \emph{GUID}\footnote{Globally Unique Identifier assigned to every
% query message generated by any node.} field same as the one of the duplicate
%message,
%  \item \emph{DetectionID} field which represents the direction of the
% connection where the duplicate was identified\footnote{This ensures the
%uniqueness of the ICM messages because as it travels through many cyclic paths,
%multiple peers will detect the duplicates and initiate an ICM message.}, and
%  \item \emph{Node Information Vector (NIV)} which contains information
% (bandwidth, CPU power, etc) about peers that propagated the ICM.
%\end{inparaenum}
%
%\paragraph{}
%Suppose $A$ detected the duplicate as depicted in Figure~\ref{figure:dcmp}. It
% then emits an ICM to $B$ and $F$, that initially contains information only
%about itself. Each peer that receives the ICM, appends its information and
%propagates it along the reverse path of the original message. Since two copies
%of ICM are sent, at some point, a peer, say peer $D$, will receive a duplicate
%ICM. Using the information in the NIVs of the ICMs, $D$, decides to cut (for
%example) the EF connection. To inform the other peers about its decision, it
%emits a \emph{Cut Message (CM)} which contains the GUID and DetectionID of the
%corresponding ICM and an additional field that identifies the connection to be
%cut. $D$, then, forwards the CM in the reverse directions from where the ICM
%arrived. Similarly CMs received by any peer are propagated toward the reverse
%path of the corresponding ICM. Eventually, either peer $E$ or peer $F$ will
%receive the CM and cut the connection, thus eliminating the cycle.
%
%Receiving a duplicate ICM denotes the existence of a cycle. The opposite is not
% true though. For example, if the cycle contains $2 \times TTL$ edges, it will
%not be detected, because the ICM messages will be discarded before they locate
%it. There is a trade-off between preserving the connectivity of the network and
%minimizing the duplicates that makes such a possibility to be safely ignored.
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/dcmp.jpeg}
%\caption{Cycle elimination methods in DCMP}
%\label{figure:dcmp}
%\end{figure}
%
%\paragraph{}
%
% TODO: SOME DISCUSSION
%
%Actually, the duplicate packet problem seems to hurt more the active nodes;
%those with higher capacities and bandwidth that contribute the most to the
%network.
The expected \emph{DCMP} behavior as far as our $3$ criteria is:
%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It return more result than LTM according to experiments in
% \cite{ZKB2008}
medium &
% Duplicates are an important fraction of the redundant overhead imposed by
% topology mismatch and thus DCMP minimizes this as possible.
% The control overhead is also one to two orders of magnitude less than LTM due
% to its ``lazy'' broadcasting of control messages (as opposed to LTM's periodic
% approach) - \cite{ZKB2008}
low &
% fully distributed method
high
\end{tabular}
}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Replication Strategies in Unstructured Peer-to-Peer Networks}

In~\cite{CS2002}, replication is used as a way 
to improve inefficient blind search.
As the number of replicas and/or cached copies increases in the network,
it would relatively easy to locate items even if the search is random.
% \cite{CS2002} aim to improve the inefficient blind search algorithm by
% replicating the data in a P2P network. 
% The main intuition behind the
% idea of replication, or using cached copies, is that as the number of copies for
% each item increases in the network, it would be easier for a search algorithm,
% even a random one, to locate these items. 
To analyze the feasibility of
such an approach, \cite{CS2002} investigates $3$ replication
strategies: uniform, proportional, and square-root allocation. In the
uniform model, the copies of items are uniformly spread over the network,
while in the proportional, items are replicated based on their query
rate, so that frequently queried items can be found more often. 
The square root is a compromise between uniform 
and proportional allocation models.
% allocation is a strategy proposed by Cohen and Shenker, which is a model between
% the uniform and proportional allocation.  
%%AD why u need to say the name here????
The overall costs for both successful and unsuccessful
searches are compared to ascertain the effectiveness of the $3$ suggested 
approaches.
% To evaluate the outcome of the replication models, 
% the overall costs of successful and unsuccessful
% searches in the network are compared. 
Experimental outcomes indicate that the uniform allocation 
minimizes the maximum search length and so it can 
reduce the time spent on unsuccessful searches.
% Results argue that the uniform allocation %%AD results argue???? --
					    %% ALSO, "search size??? See above
% model minimizes the maximum search size, therefore reduces the time spent on an
% unsuccessful search. 
The proportional strategy effectively decreases the search time 
for popular items, but suffers when needing to locate the rare entities.
% The proportional model, on the other hand, promotes the
% more frequently queried items by replicating them more and therefore decreases the
% search time for popular items, but suffers when needing to locate the rare
% items. 
When it comes to expected successful search size, it is the same for 
for both uniform and proportional models and any approach in between 
to always behave much better.
% The authors also claim that the expected successful search size is the
% same for uniform and proportional models, and any approach between them would
% always behave much better. 
The square root allocation  aims at minimizing the 
expected search size for successful queries in \p\ networks.
% Finally, they propose the square root allocation
% approach, which is a replication strategy that minimizes the expected search
% size of successful queries in P2P networks.
%%
The table below outlines how the $3$ strategies fare:
%%
\begin{center}
{\footnotesize
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Uniform Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% When item is created, replicate its key in a fixed number of hosts.
low &
%
medium \\
\emph{Proportional Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% for each query, replicate the key in a fixed number of hosts (need to know or
% estimate the query rate)
medium &
%
low \\
\emph{Square Root Replication Allocation} &
% All (strictly) in-between strategies are (strictly) better than Uniform and
% Proportional - replication theory
medium &
% Assuming that each query keeps track of the search size then each time a query
% is finished the object is copied to a number of sites proportional to the
% number of probes that the search required.
medium &
% e.g. path replication is easy to scale, just detect the path along which the
% query ultimately got fulfilled
medium \\
\end{tabular}
}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Narada}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Landmark Binning (LM)}\label{sec:landmark_binning}
% \begin{figure*}
% \centering
%   \includegraphics[scale=0.4]{img/algorithms/landmark_binning}
% \caption{Example 2D coordinate overlay and a sample routing path from node D to
% (x,y).}
% \label{fig:landmark_binning}
% \end{figure*}

\emph{Landmark Binning}~\cite{RHMKS2002} partitions close-by nodes 
into bins based on their distance from well known anchor nodes across the
Internet.%, as shown in Figure~\ref{fig:landmark_binning}.
To detect locality, peers mainly use network latency (i.e. \emph{RTT}).
%  as a measurement technique. 
Despite the fact that such delays are not always accurate,
they are used in~\cite{RHMKS2002} for they are 
non-intrusive, transparent and easy to apply.
%%
For the binning to work, a few anchor servers with known
physical locations need to be installed in strategic positions 
across the the Internet. 
It is conjectured~\cite{RHMKS2002} that $12$ such servers can prove
sufficient for the task.
An arriving node measures its distance from these landmarks
and unilaterally decides to join a specific bin based on its measurements.
Specifically, the node measures its round-trip time to each of the landmarks and
orders the resulting \emph{RTT}-values in a decreasing order. 
%%AD I do not understand what the following sentence says..
%%	for each peer there is a different bin right? 
The ordering represents a \emph{bin},
in the sense of close-by nodes having the same landmark ordering and hence
belong to the same bin. 
%%
%%AD I think the above sentence is the main information related in this 
%%   piece of description so it requires a bit better description...
Should there $m$ landmarks be adopted, potentially $m!$  different bins exist.
% This means that a landmark system consisting of $m$ such
% nodes results in $m!$ potential different bins.
%%
The operation of the method is independent of the model 
incorporated by the overlay network and thus it can be
applied with no significant changes to 
both structured and unstructured \p\ systems. 
% \cite{RHMKS2002} has the detailed description of the algorithm for
% both architectures. %%AD obviously!!!!
%%
%%AD why is it important to say this about CDNs???
% Landmark binning is also considered as a good candidate for
% content distribution networks. 
The main disadvantage of the approach is that 
